IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-20 ms.tex
I finalized which source was used as the reference for 2MASS 1821.

\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi? }
\affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
\email{eas342@email.arizona.edu}

@@

\section{Observations}
We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
For 2MASS J1821, we observed a simultaneous reference - (I think it was 2MASS 18212622+1414064, J=12.58, H=11.97, K=11.82  at a distance of 30.1\arcsec\ or was it 2MASS 18212622+1414064, J=11.25, H=10.91, K=10.85 at a distance of 19.1\arcsec)?
\input{observing_table.tex}

>>>>

\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi }
\affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
\email{eas342@email.arizona.edu}

@@

\section{Observations}
We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
For 2MASS J1821, we observed a simultaneous reference - (I think it was 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24 \arcsec. 
%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
\input{observing_table.tex}
